Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-21 doc/Paper/main.tex
pass through the whole paper

  \subsection{Parameter constraints}\label{ssec:methods.constr}
    In order to derive constraints on HOD, cosmological and systematics parameters, we assume the joint likelihood of all auto- and cross power spectra to be Gaussian 
    \begin{align}
      \mathscr{L}(D \vert \theta) = \frac{1}{[(2\pi)^{d}\det{\mathsf{C}}]^{\sfrac{1}{2}}} e^{-\frac{1}{2}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})^{\mathrm{T}}\mathsf{C}^{-1}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})}.
      \label{eq:likelihood}
    \end{align}
    The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and is kept constant during parameter estimation \citep{2019OJAp....2E...3K}.
    We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}. In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{0}, \allowbreak \, M_{0, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}. The remaining parameters account for photometric redshift uncertainties as described in Sec.~\ref{sssec:methods.theory.photoz_syst}. We perform additional analyses in which we separately allow for variations in the amplitude $A_{\mu}$ of the magnification bias kernel $W_{\mu}$ and the cosmological parameters $\Omega_{c}$ and $\sigma_{8}$, where $\Omega_{c}$ is the the fractional cold matter density today and $\sigma_{8}$ denotes the r.m.s. of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc. For all sampled parameters, we assume flat, uniform priors. The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}. The remaining HOD parameters are set to $\alpha = 1.0$ and $\sigma_{\log M} = 0.4$. Unless stated otherwise, we further fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e. $\Omega_{b}=0.0493$, $\Omega_{c}=0.264$, $h=0.6736$, $n_{s}=0.9649$ and $\sigma_{8}=0.8111$ (see the fourth column in Tab.~2 in \cite{Planck:2018}).

    We fit all power spectra up to a maximal angular multipole $\ell_{\mathrm{max}}$ approximately corresponding to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$, as determined through the Limber relation $k_{\mathrm{max}} = \sfrac{\ell_{\mathrm{max}}}{\chi(z)}$. For the auto power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}. For the cross correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.

@@

  \subsection{Covariance matrix}\label{ssec:results.covariance}
    We estimate the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}. In Fig.~\ref{fig:covariance-contributions}, we split the auto-covariances for the four redshift bins into the Gaussian, non-Gaussian and SSC contributions. As can be seen, the Gaussian contribution is dominant on large scales while the non-Gaussian part becomes important at small scales and low redshift. The high redshift bins are mostly insensitive to non-Gaussian contributions to the covariance. Finally, the SSC is subdominant in all cases. This is mainly due to the number density correction in Eq.~\ref{eq:ps-resp}, which significantly suppresses any SSC contributions to the total covariance.
    \begin{figure}
      \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
        \caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
      \end{center}
    \end{figure}

@@

      In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ obtained in our analysis. To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs. As can be seen, we find that, within or uncertainties, the data prefer both a constant $M_{\mathrm{min}}$ and $M_{1}$. This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift since galaxies will only form in the most massive halos at early times. We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}. Finally we see from Tab.~\ref{tab:constraints_robustness} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low. This is a feature of our HOD model enforcing that no halo can host satellites if it does not contain a central galaxy, regardless of $M_{0}(z)$ (see Eq.~\ref{eq:ng_hod}). Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses, i.e. the data constrain the maximal $M_{0}(z)$ to be of the order of $M_{\mathrm{min}}(z)$, but our HOD model does not allow us to distinguish between masses smaller than $M_{\mathrm{min}}(z)$.

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
\caption{Fiducial constraints on HOD parameters obtained in this work. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-fid-hod}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag.pdf}
\caption{Measured auto- and cross power spectra considered in our analysis. The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
\label{fig:cls-best-fit}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}} 
\caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.} 
\label{fig:hod-params-z-dep}
\end{center}
\end{figure}

\subsubsection{Robustness to modeling and data choices}

In order to test the robustness of our fiducial HOD constraints to implementation and data choices, we compare the constraints from several analysis variants, as described in the following. A summary of all robustness tests performed and the respective constraints on HOD parameters and extended models can be found in Tab.~\ref{tab:constraints_robustness}.

\begin{sidewaystable}
\caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
\begin{center}
\begin{tabular}{ccccccccc}
\hline\hline 
Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.491\substack{+2.09 \\ -2.02}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.933\substack{+2.67 \\ -2.56}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
G cov & $\sfrac{87.2}{80}$ $(0.27)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.645 \\ -0.652}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.624 \\ -0.771}$ & $11.78 \pm 0.13$ & $-0.108\substack{+0.727 \\ -0.940}$ & $12.93 \pm 0.16$ & - & - & - \\
bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.354\substack{+2.34 \\ -2.25}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.624\substack{+2.87 \\ -2.75}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.97}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.270\substack{+2.05 \\ -1.88}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.82\substack{+2.87 \\ -2.59}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
pz = \texttt{Ephor} & $\sfrac{107.2}{80}$ $(0.023)$ & $0.895\substack{+1.97 \\ -2.03}$ & $12.15 \pm 0.17$ & $2.64\substack{+2.71 \\ -2.80}$ & $13.40\substack{+0.23 \\ -0.22}$ & - & - & - \\
pz = \texttt{DEmP} & $\sfrac{105.4}{80}$ $(0.031)$ & $0.616\substack{+1.90 \\ -1.88}$ & $12.07\substack{+0.17 \\ -0.16}$ & $2.29\substack{+2.59 \\ -2.55}$ & $13.30\substack{+0.22 \\ -0.21}$ & - & - & - \\
pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
fiducial magn. & $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.14 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
fit cosmo & $\sfrac{84.4}{78}$ $(0.29)$ & $0.0143\substack{+2.72 \\ -2.53}$ & $11.79\substack{+0.27 \\ -0.24}$ & $1.63\substack{+3.44 \\ -3.20}$ & $12.96\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.807\substack{+0.149 \\ -0.143}$ \\
 \hline \hline
\end{tabular}
\end{center}
\end{sidewaystable}

>>>>

  \subsection{Parameter constraints}\label{ssec:methods.constr}
    In order to derive constraints on HOD, cosmological and systematics parameters, we assume the joint likelihood of all auto- and cross-power spectra to be Gaussian 
    \begin{align}
      \mathscr{L}(D \vert \theta) = \frac{1}{[(2\pi)^{d}\det{\mathsf{C}}]^{\sfrac{1}{2}}} e^{-\frac{1}{2}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})^{\mathrm{T}}\mathsf{C}^{-1}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})}.
      \label{eq:likelihood}
    \end{align}
    The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and is kept constant during parameter estimation \citep{2019OJAp....2E...3K}.
    We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}. In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{0}, \allowbreak \, M_{0, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}. The remaining parameters account for photometric redshift uncertainties as described in Sec.~\ref{sssec:methods.theory.photoz_syst}. We perform additional analyses in which we separately allow for variations in the amplitude $A_{\mu}$ of the magnification bias kernel $W_{\mu}$ and the cosmological parameters $\Omega_{c}$ and $\sigma_{8}$, where $\Omega_{c}$ is the the fractional cold matter density today and $\sigma_{8}$ denotes the r.m.s. of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc. For all sampled parameters, we assume flat, uniform priors. The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}. The remaining HOD parameters are set to $\alpha = 1.0$ and $\sigma_{\log M} = 0.4$. Unless stated otherwise, we further fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e. $\Omega_{b}=0.0493$, $\Omega_{c}=0.264$, $h=0.6736$, $n_{s}=0.9649$ and $\sigma_{8}=0.8111$ (see the fourth column in Tab.~2 in \cite{Planck:2018}).

    We fit all power spectra up to a maximal angular multipole $\ell_{\mathrm{max}}$ approximately corresponding to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$, as determined through the Limber relation $k_{\mathrm{max}} = \sfrac{\ell_{\mathrm{max}}}{\chi(z)}$. For the auto power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}. For the cross-correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.

@@

  \subsection{Covariance matrix}\label{ssec:results.covariance}
    We estimate the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}. In Fig.~\ref{fig:covariance-contributions}, we split the auto-covariances for the four redshift bins into the Gaussian, non-Gaussian and SSC contributions. As can be seen, the Gaussian contribution is dominant on large scales while the non-Gaussian part becomes important at small scales and low redshift. The high redshift bins are mostly insensitive to non-Gaussian contributions to the covariance. Finally, the SSC is subdominant in all cases. This is mainly due to the number density correction in Eq.~\ref{eq:ps-resp}, which significantly suppresses any SSC contributions to the total covariance.
    \begin{figure}
      \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
      \end{center}
    \end{figure}

@@

      In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ obtained in our analysis. To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs. As can be seen, we find that, within or uncertainties, the data prefer both a roughly constant $M_{\mathrm{min}}$ and $M_{1}$. This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift, since galaxies will only form in the most massive halos at early times. We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}. Finally we see from Tab.~\ref{tab:constraints_robustness} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low \todo{This table doesn't really contain information about $M_0$.}. This is a feature of our HOD model enforcing that no halo can host satellites if it does not contain a central galaxy, regardless of $M_{0}(z)$ (see Eq.~\ref{eq:ng_hod}). Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses. I.e. the data constrain the maximal $M_{0}(z)$ to be of the order of $M_{\mathrm{min}}(z)$, but our HOD model does not allow us to distinguish between masses smaller than $M_{\mathrm{min}}(z)$. Physically, this means that the data show preference for a model in which all halos massive enough to host a central galaxy are likely to host satellites too.
      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
          \caption{Fiducial constraints on HOD parameters obtained in this work. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
          \label{fig:constraints-fid-hod}
        \end{center}
      \end{figure}

      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag.pdf}
          \caption{Measured auto- and cross-power spectra considered in our analysis. The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross-power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
          \label{fig:cls-best-fit}
        \end{center}
      \end{figure}

      \begin{figure}
        \begin{center}
          \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
          \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
          \caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty. \todo{could we make the samples semi-transparent so we see how they bunch up around the best-fit?}} 
          \label{fig:hod-params-z-dep}
        \end{center}
      \end{figure}

    \subsubsection{Robustness to modeling and data choices}
      In order to test the robustness of our fiducial HOD constraints to implementation and data choices, we compare the constraints from several analysis variants as follows. A summary of all robustness tests performed and the respective constraints on HOD parameters and extended models can be found in Tab.~\ref{tab:constraints_robustness}.

      \begin{sidewaystable}
        \caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. \todo{it would be good to specify what the error bars are. I imagine they're watershed errors (i.e. values with equal probability enclosing 60\% of $p$. Is that correct?} The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
        \begin{center}
          \begin{tabular}{ccccccccc}
            \hline\hline 
            Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
            fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.491\substack{+2.09 \\ -2.02}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.933\substack{+2.67 \\ -2.56}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
            auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
            G cov & $\sfrac{87.2}{80}$ $(0.27)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
            G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
            no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.645 \\ -0.652}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
            no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.624 \\ -0.771}$ & $11.78 \pm 0.13$ & $-0.108\substack{+0.727 \\ -0.940}$ & $12.93 \pm 0.16$ & - & - & - \\
            bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.354\substack{+2.34 \\ -2.25}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.624\substack{+2.87 \\ -2.75}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
            bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.97}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
            pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.270\substack{+2.05 \\ -1.88}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.82\substack{+2.87 \\ -2.59}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
            pz = \texttt{Ephor} & $\sfrac{107.2}{80}$ $(0.023)$ & $0.895\substack{+1.97 \\ -2.03}$ & $12.15 \pm 0.17$ & $2.64\substack{+2.71 \\ -2.80}$ & $13.40\substack{+0.23 \\ -0.22}$ & - & - & - \\
            pz = \texttt{DEmP} & $\sfrac{105.4}{80}$ $(0.031)$ & $0.616\substack{+1.90 \\ -1.88}$ & $12.07\substack{+0.17 \\ -0.16}$ & $2.29\substack{+2.59 \\ -2.55}$ & $13.30\substack{+0.22 \\ -0.21}$ & - & - & - \\
            pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
            fiducial magn. & $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
            fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.14 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
            fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
            fit cosmo & $\sfrac{84.4}{78}$ $(0.29)$ & $0.0143\substack{+2.72 \\ -2.53}$ & $11.79\substack{+0.27 \\ -0.24}$ & $1.63\substack{+3.44 \\ -3.20}$ & $12.96\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.807\substack{+0.149 \\ -0.143}$ \\
            \hline \hline
          \end{tabular}
        \end{center}
      \end{sidewaystable}

      As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross-power spectra. However, cross-correlations between redshift bins are susceptible to photometric redshift errors, such as outliers. In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross-power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross-power spectra. Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone. As can be seen, the constraints from auto-spectra and from both auto- and cross-power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis. Furthermore, we see that the constraining power on HOD parameters is mostly unaffected by including the cross-power spectra. As a final consistency check between auto- and cross-power spectra we test how well the auto-spectra predict the cross-spectra. To this end we compute the $\chi^{2}$ between the observed auto- and cross-power spectra and the theoretical predictions derived from auto power spectra only. As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test. We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross-power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}). This shows that the auto power spectra are able to predict the cross-power spectra and provides further confirmation of their consistency.
